Explore resilience evi

### 2017-11-24 analysis/evi/explore_resilience.Rmd
update
update robust anovas

@@

@@

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest 
  out$pha <- pha
  out$phb <- phb
  out$phab <- phab

  print(out_ra)
  print(phRWS2)

>>>>

  set.seed(123)

@@

  out_raTrimmed <- t2way(formulaFull, data = df)

@@

  phtrimmed <- mcp2atm(formulaFull, data=df)

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$raTrimmed <- out_raTrimmed
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest 
  out$pha <- pha
  out$phb <- phb
  out$phab <- phab

  print(cat('\n Robust M-Anova \n'))
  print(out_ra)
  print(cat('\n Robust Trimmed \n'))
  print(out_raTrimmed)
  print(cat('\n post hoc Mhuber \n'))
  print(phRWS2)
  print(cat('\n post hoc Trimmed means \n'))
  print(phtrimmed)
